\documentclass[conference]{IEEEtran}

\makeatletter
% IEEEtran.cls defines \labelindent for backward compatibility reasons
% Undefine \labelindent to allow the use of package enumitem
\let\labelindent\relax
\makeatother

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{array}
\usepackage{balance}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{color}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[para]{footmisc}
\usepackage{framed}
\usepackage[pdftex]{graphicx}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{url}


% SQUEEZE
%\addtolength{\parskip}{-1pt}


\definecolor{lightred}{RGB}{150,0,0}
\definecolor{lightgreen}{RGB}{0,150,0}
\definecolor{lightblue}{RGB}{0,0,150}

\lstdefinelanguage{diff}{
  morecomment=[f][\color{lightblue}]{diff },
  morecomment=[f][\color{lightblue}]{index },
  morecomment=[f][\color{lightblue}]{@@},     % group identifier
  morecomment=[f][\color{lightred}]-,         % deleted lines
  morecomment=[f][\color{lightgreen}]+,       % added lines
  morecomment=[f][\color{lightblue}]{---},    % Diff header lines (must appear after +,-)
  morecomment=[f][\color{lightblue}]{+++},
}
\hyphenation{}

\newcommand{\attn}[1]{{\color{red}#1}}
\newcommand{\desc}[1]{{\emph{\color{blue}#1}}}
\newcommand{\needcite}{\attn{\tiny{[cite]}}}
\newcommand{\todo}[1]{\strut\smash{\colorbox{yellow}{\bf TODO: #1}}}

\begin{document}
\title{Modeling Changeset Topics for Feature Location}
\author{
    \IEEEauthorblockN{
        Christopher S.\ Corley,
        Kelly L.\ Kashuda
    }
    \IEEEauthorblockA{
        The University of Alabama\\
        Tuscaloosa, AL, USA\\
        \{cscorley, klkashuda\}@ua.edu
    }

    \and

    \IEEEauthorblockN{
        Nicholas A.\ Kraft
    }
    \IEEEauthorblockA{
        ABB Corporate Research\\
        Raleigh, NC, USA\\
        nicholas.a.kraft@us.abb.com
    }
}


\maketitle

\begin{abstract}
Feature location is a program comprehension activity in which a developer
inspects source code to locate the classes or methods that implement a feature of interest.
Many feature location techniques (FLTs) are based on text retrieval models, and
in such FLTs it is typical for the models to be trained on source code snapshots.
However, source code evolution leads to model obsolescence and
thus to the need to retrain the model from the latest snapshot.
In this paper, we introduce a topic-modeling-based FLT in which the model
is built incrementally from source code history.
By training an online learning algorithm using changesets, the FLT
maintains an up-to-date model without incurring the non-trivial computational cost associated with retraining traditional FLTs.
Overall, we studied over 1,200 defects and features from 14 open-source Java projects.
We also present a historical simulation that demonstrates how the FLT performs as a project evolves.
Our results indicate that the accuracy of a changeset-based FLT is similar to that of a snapshot-based FLT, but without the retraining costs.
\end{abstract}

\begin{IEEEkeywords}
program comprehension;
feature location;
topic modeling;
mining software repositories;
changesets
\end{IEEEkeywords}

\section{Introduction}
\label{sec:intro}
\input{sec_intro}

\section{Background \& Related Work}
\label{sec:related}
\input{sec_related}

\section{Changeset Topic Modeling}
\label{sec:changeset}
\input{sec_changeset}

\section{Study}
\label{sec:study}
\input{sec_study}

\section{Threats To Validity}
\label{sec:threats}
\input{sec_threats}

\section{Conclusion}
\label{sec:conclusion}
\input{sec_conclusion}

% \section*{Acknowledgment}
% %We thank the anonymous reviewers for their insightful comments and helpful suggestions.
% This material is based upon work supported
% by the National Science Foundation under Grant No.\ 1156563. % REU grant for KLK

%\newpage \ \newpage
\bibliographystyle{IEEEtran}
\bibliography{paper}

\end{document}
